Nirdizati: A Web-Based Tool for\\ Predictive Process Monitoring

### 2017-07-28 BPM17-demo-paper/paper.tex
revise Kafka description

\begin{figure}[t!]%[H]
	\centering
	 \includegraphics[width=0.9\textwidth]{img/nirdizati-frontend}
	%\includegraphics[width=0.7\textwidth]{img/nirdizati-training}
	\caption{Front-end of Nirdizati Training.}
	\label{fig:nirdizati-frontend}
	\vspace{-0.5\baselineskip}
\end{figure}
\begin{figure}[b!]%[H]
	\centering
	 \includegraphics[width=0.9\textwidth]{img/nirdizati-training-architecture-rev}
	%\includegraphics[width=0.7\textwidth]{img/nirdizati-training}
	\caption{High-level overview of Nirdizati Training.}
	\label{fig:nirdizati-training}
	\vspace{-0.5\baselineskip}
\end{figure}

@@

\section{Nirdizati Runtime} \label{sec:runtime}
Once the predictive models have been created, they are used by the Runtime component to make predictions on ongoing cases.
As input, Nirdizati Runtime takes a stream of events produced by information systems that register the tasks performed in organizations (\figurename~\ref{fig:dfd_0}).
For scalable and fault-tolerant processing, we use the open-source stream processing platform Apache Kafka.
Events belonging to the same process case are collated to make predictions for that case.
A web server communicates with a predictive engine that queries the predictive models obtained by Nirdizati Training.
The results from all predictors are joined and visualized in a dashboard-based interface, which supports several visualization options.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{img/nirdizati-runtime}
	\caption{Main view of Nirdizati Runtime.}
	\label{fig:nirdizati-runtime}
	\vspace{-0.5\baselineskip}
\end{figure}
%\vspace{-\baselineskip}

>>>>

\begin{figure}[t!]%[H]
	\centering
	 \includegraphics[width=0.8\textwidth]{img/nirdizati-frontend}
	%\includegraphics[width=0.7\textwidth]{img/nirdizati-training}
	\caption{Front-end of Nirdizati Training.}
	\label{fig:nirdizati-frontend}
	\vspace{-0.5\baselineskip}
\end{figure}
\begin{figure}[b!]%[H]
	\centering
	 \includegraphics[width=0.8\textwidth]{img/nirdizati-training-architecture-rev}
	%\includegraphics[width=0.7\textwidth]{img/nirdizati-training}
	\caption{High-level overview of Nirdizati Training.}
	\label{fig:nirdizati-training}
	\vspace{-0.5\baselineskip}
\end{figure}

@@

\section{Nirdizati Runtime} \label{sec:runtime}
Once the predictive models have been created, they are used by the Runtime component to make predictions on ongoing cases.
Nirdizati Runtime takes a stream of events produced by an organization’s information systems, transforms it into a stream of predictions, and visualizes those predictions in a web-based dashboard.
The transformation is implemented using the dataflow pipeline in \figurename~\ref{fig:dfd_0}, in which the ``predictor'' components are the predictive models from Nirdizati Training.
The pipeline is built atop the the open-source Apache Kafka stream processing platform; the ``topic'' components are network-accessible queues of JSON messages with publisher/subscriber support. This allows the computationally intense work of the predictors to be distributed across a cluster of networked computers, providing scalability and fault-tolerance.
The ``collator'' component accumulates the sequence of events-to-date for each case, such that (for intra-case predictive monitoring) the prediction is a stateless function of only of the (static) trained predictive model and this case history.  This statelessness is what allows the predictors to be freely duplicated and distributed.  The ``joiner'' component composes the original event with the various predictions, ready for display on the dashboard.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{img/nirdizati-runtime}
	\caption{Main view of Nirdizati Runtime.}
	\label{fig:nirdizati-runtime}
	\vspace{-0.5\baselineskip}
\end{figure}
%\vspace{-\baselineskip}
